Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-29 manuscript.Rmd
reverse coding

df2 <-  
df %>% 
  mutate(
    across(recode_99s$rowname, ~ na_if(.x, 99))
  )
```

>>>>

df <-  
df %>% 
  mutate(
    across(recode_99s$rowname, ~ na_if(.x, 99))
  )

# reverse coding
negative_keyed_items <- c('perceiver_trait15', 'perceiver_trait8',
                          'perceiver_trait21', 'perceiver_trait25',
                          'perceiver_trait10', 'perceiver_trait18',
                          'perceiver_trait4', 'perceiver_trait16',
                          'target_trait15', 'target_trait8',
                          'target_trait21', 'target_trait25',
                          'target_trait10', 'target_trait18',
                          'target_trait4', 'target_trait16',
                          'judgment_trait15', 'judgment_trait8',
                          'judgment_trait21', 'judgment_trait25',
                          'judgment_trait10', 'judgment_trait18',
                          'judgment_trait4', 'judgment_trait16')

df <- 
df %>% 
  mutate(
    across(all_of(negative_keyed_items), subtract_8)
  )
